### 2019-10-31 figures/07_model-selection.Rmd
autoselect best model, cleaner model diagnostics

```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$R2)
# lapply(re_brms, function(x) x $formula) 
# re_brms[[2]]$formula
best_tp        <- 2 # 2 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
# re_brms[[8]]$formula
# brms::bayes_R2(re_brms[[8]])

best_tn        <- 8 # 11 is best tn model with random effects
fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)

>>>>

```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
# autoselect best model
re_names <- unlist(lapply(re_brms, function(x) 
  get_re_text(as.character(x$formula)[[1]])))[1:(length(re_brms)/2)]
best_tp <- loo_compare(
  lapply(seq_len(length(re_brms)/2), function(x) re_brms[[x]]$loo))
best_tp <- which(re_names == row.names(best_tp)[1])

fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# autoselect best tn model
re_names <- unlist(lapply(re_brms, function(x) 
  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
                                                  length(re_brms))]
best_tn <- loo_compare(
  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
         function(x) re_brms[[x]]$loo))
best_tn <- which(re_names == row.names(best_tn)[1])

fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
# setwd("figures")
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))

### 2019-10-31 tables/03_model_summary.Rmd
autoselect best model, cleaner model diagnostics

r2_re <- dplyr::bind_rows(
  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x))))
r2_re$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
r2_re$response <- c(rep("tp", nrow(r2_re) / 2), rep("tn", nrow(r2_re) / 2))
r2_re <- dplyr::filter(r2_re, term != "rowvcropvpct")

sort_loo <- function(x){
  x_df       <- as.data.frame(x)
  x_df$index <- row.names(x_df)
  x_df$index <- as.numeric(stringr::str_extract(x_df$index, "\\d+"))
  arrange(x_df, index)
}

loo_re <- rbind(
  sort_loo(loo_compare(loo(re_brms[[1]]),
                       loo(re_brms[[3]]), loo(re_brms[[4]]),
                       loo(re_brms[[5]]), 
                       loo(re_brms[[6]]))),
  sort_loo(loo_compare(loo(re_brms[[7]]),
                       loo(re_brms[[9]]), loo(re_brms[[10]]),
                       loo(re_brms[[11]]), 
                       loo(re_brms[[12]])))
  ) %>%
  arrange(index)

dt           <- r2_re
dt$elpd_diff <- loo_re$elpd_diff
dt <- dplyr::select(dt, 
                    response, term, r2 = Estimate, elpd_diff)
dt <- dt[order(dt$response, dt$elpd_diff, decreasing = c(TRUE, FALSE)),]

>>>>

# filter out row crop from r2_brms
predictors <- unlist(lapply(re_brms, function(x) get_re_text(
  as.character(x$formula)[[1]])))
re_brms    <- re_brms[-1 * which(predictors == "rowvcropvpct")]
predictors <- unlist(lapply(re_brms, function(x) get_re_text(
  as.character(x$formula)[[1]])))

# get responses
response <- unlist(lapply(re_brms, function(x) get_re_response(
  as.character(x$formula)[[1]])))

loo_re <- rbind(
  loo_compare(lapply(which(response == "tp"), function(x) re_brms[[x]]$loo)), 
  loo_compare(lapply(which(response == "tn"), function(x) re_brms[[x]]$loo))) 
loo_re_df            <- data.frame(loo_re)
row.names(loo_re_df) <- NULL
loo_re_df$term       <- row.names(loo_re)
loo_re_df$response   <- response

dt <- dplyr::bind_rows(lapply(re_brms, function(x) x$R2))
dt <- left_join(loo_re_df, dt, by = c("term", "response"))
dt <- dplyr::select(dt, 
                    response, term, r2 = Estimate, elpd_diff)
dt <- dt[order(dt$response, dt$elpd_diff, decreasing = c(TRUE, FALSE)),]
